---
title: "In-Class Kaggle House Prediction Project"
author: "Seth Harrison"
date: 'Last compiled: `r format(Sys.time(), "%b %d, %Y")`'
output: ioslides_presentation
---

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
library(tidyverse)
library(MASS)
library(caret)
library(earth)
knitr::opts_chunk$set(echo = FALSE)
housedata <- read.csv("housedata.csv", 
                      colClasses = c(id = "character", date = "character", 
                                     yr_built = "character", zipcode = "factor", grade = "factor"))
housedata$date <- as.Date(housedata$date, "%Y%m%d")
housedata$waterfront <- factor(housedata$waterfront, labels = c("No", "Yes"))
housedata$condition <- factor(housedata$condition, labels = c("poor", "fair", "average", "good", "very good"))
housedata$yr_renovated <- ifelse(housedata$yr_renovated == 0, housedata$yr_built, housedata$yr_renovated)
housedata$yr_built <- as.Date(ISOdate(housedata$yr_built, 9, 1))  # Complete Year, Sept 1
housedata$yr_renovated <- as.Date(ISOdate(housedata$yr_renovated, 9, 1))  # Last renovated Year, Sept 1
housedata <- housedata[, -1]
#### Perform same steps with test set
housedataT <- read.csv("housedataTEST.csv", 
                      colClasses = c(id = "character", date = "character", 
                                     yr_built = "character", zipcode = "factor", grade = "factor"))
housedataT$date <- as.Date(housedataT$date, "%Y%m%d")
housedataT$waterfront <- factor(housedataT$waterfront, labels = c("No", "Yes"))
housedataT$condition <- factor(housedataT$condition, labels = c("poor", "fair", "average", "good", "very good"))
housedataT$yr_renovated <- ifelse(housedataT$yr_renovated == 0, housedataT$yr_built, housedataT$yr_renovated)
housedataT$yr_built <- as.Date(ISOdate(housedataT$yr_built, 9, 1))  # Complete Year, Sept 1
housedataT$yr_renovated <- as.Date(ISOdate(housedataT$yr_renovated, 9, 1))  # Last renovated Year, Sept 1
housedataT <- housedataT[, -1]

mod1 <- stepAIC(lm(price ~ . - sqft_lot15, data = housedata))

housedataModified <- housedata %>%
  filter(price < 2000000) %>%
  filter(sqft_living < 12000)
mod2 <- stepAIC(lm(price ~ ., data = housedataModified))

mod3 <- lm(price ~ . + poly(sqft_living, 3, raw = TRUE), data = housedata)

mod4 <- earth(price ~ . - sqft_lot15, data = housedata, degree = 2)

```

## Initial thoughts

* The first approach I took to reducing RMSE was just looking at what variables weren't significant and I found that just by cutting sqft_lot15 the RMSE could be reduced to 143,000 and adjusted r-squared value of .8349.

```
mod1 <- stepAIC(lm(price ~ . - sqft_lot15, data = housedata))
```

```{r}
summary(mod1)[9]
```


## Removing Large Values

* Then I tried removing higher priced homes from the data as there were only a few hundred of them and they could possibly be skewing the data. Ultimately this only resulted in an RMSE reduction of 300 bringing me down to 142,700.

```
housedataModified <- housedata %>%
  filter(price < 2000000) %>%
  filter(sqft_living < 12000)
mod2 <- stepAIC(lm(price ~ ., data = housedataModified))
```

```{r}
summary(mod2)[9]
```

## Creating Polynomial Terms

* I expected Polynomial Terms to help capture some of the remaining variance and they did so but I discovered quickly that including too many polynomial terms would hurt me and after fitting five third-order polynomial terms and having an RMSE over a million I tried keeping it simple and only created a polynomial of order three out of the sqft_living.

```
mod3 <- lm(price ~ . + poly(sqft_living, 3, raw = TRUE), data = housedata)
```

```{r}
summary(mod3)[9]
```

## Multivariate Regression Spline

* I tried creating a new predictor by compressing grade into three categories, though when this didn't find success I decided to use a multivariate regression spline to create a polynomial model that can capture more of the variance than my earlier approach to using polynomials. The earth package allows the easy creation of MARS models and got me my best results so far with a RMSE of around 126,648 and an R-Squared value of .8829.

```
mod4 <- earth(price ~ . - sqft_lot15, data = housedata, degree = 2)
```

```{r}
summary(mod4)[2]
```

